Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-29 draft/ms_v5.tex
Draft for Table1

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the workflow of \synpipe{}.
        Gray boxes indicate required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
        synthetic objects into single-frame images. 
        Below the blue box, we show an HSC image before and after the insertion of 
        synthetic galaxies. 
        The positions of synthetic objects are highlighted with green circles. 
        Red boxes depict the image coadding and multi-band measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py}. 
        At the bottom left, we show a \coadd{} image which contains synthetic galaxies. 
        On the right hand side, we show the spatial relation between \texttt{tracts},
        \texttt{patches}, and \texttt{visits}. 
        The red colored box corresponds to one \texttt{tract} which has an area of 
        about 1.5 deg$^2$. 
        Large colored circles are \texttt{visits} (also commonly known as "pointings") 
        with small rectangles representing CCDs. 
        \texttt{patches} are represented by black dashed lines. 
        One \texttt{tract} typically contains 81 \texttt{patches}.
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the workflow of \synpipe{}.
        Gray boxes indicate required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
        synthetic objects into single-frame images. 
        Below the blue box, we show an HSC image before and after the insertion of 
        synthetic galaxies. 
        The positions of synthetic objects are highlighted with green circles. 
        Red boxes depict the image coadding and multi-band measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py}. 
        At the bottom left, we show a \coadd{} image which contains synthetic galaxies. 
        On the right hand side, we show the spatial relation between \texttt{tracts},
        \texttt{patches}, and \visits{}. 
        The red colored box corresponds to one \tract{} which has an area of 
        about 1.5 deg$^2$. 
        Large colored circles are \visits{} (also commonly known as ``pointings'') 
        with small rectangles representing CCDs. 
        \texttt{patches} are represented by black dashed lines. 
        One \tract{} typically contains 81 \texttt{patches}.
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & Precision & 0.016 & 0.017 & 0.019 & 0.023 & 0.029 & 0.043 & 0.078 \\
        &      & Accuracy  & 0.008 & 0.009 & 0.009 & 0.009 & 0.008 & 0.007 & $\minus 0.003$ \\
        \cline{3-10}
        & 0.70 & Precision & 0.016 & 0.018 & 0.019 & 0.021 & 0.026 & 0.039 & 0.091 \\
        &      & Accuracy  & 0.007 & 0.006 & 0.006 & 0.005 & 0.004 & 0.003 & $\minus 0.002$ \\
    \hline
    $r$ & 0.45 & Precision & 0.021 & 0.023 & 0.024 & 0.025 & 0.027 & 0.035 & 0.064 \\
        &      & Accuracy  & 0.011 & 0.011 & 0.012 & 0.011 & 0.012 & 0.011 & 0.011 \\
        \cline{3-10}
        & 0.70 & Precision & 0.026 & 0.029 & 0.031 & 0.034 & 0.041 & 0.054 & 0.090 \\
        &      & Accuracy  & 0.009 & 0.009 & 0.009 & 0.009 & 0.009 & 0.006 & 0.001 \\    
    \hline
    $i$ & 0.45 & Precision & 0.015 & 0.015 & 0.017 & 0.018 & 0.020 & 0.030 & 0.047 \\
        &      & Accuracy  & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 \\
        \cline{3-10}
        & 0.70 & Precision & 0.012 & 0.013 & 0.014 & 0.016 & 0.022 & 0.043 & 0.050 \\
        &      & Accuracy  & 0.001 & 0.002 & 0.002 & 0.002 & 0.002 & 0.001 & $\minus 0.012$ \\    
    \hline
    $z$ & 0.45 & Precision & 0.011 & 0.013 & 0.014 & 0.016 & 0.025 & 0.053 & 0.094 \\
        &      & Accuracy  & 0.002 & 0.002 & 0.002 & 0.003 & 0.003 & 0.005 & $\minus 0.001$ \\
        \cline{3-10}
        & 0.70 & Precision & 0.019 & 0.020 & 0.021 & 0.024 & 0.038 & 0.071 & 0.104 \\
        &      & Accuracy  & 0.003 & 0.003 & 0.003 & 0.004 & 0.005 & 0.003 & $\minus 0.010$ \\    
    \hline
    $y$ & 0.45 & Precision & 0.017 & 0.017 & 0.021 & 0.033 & 0.074 & 0.138 & -- \\
        &      & Accuracy  & 0.006 & 0.006 & 0.006 & 0.006 & 0.000 & $\minus 0.001$ & -- \\
        \cline{3-10}
        & 0.70 & Precision & 0.019 & 0.019 & 0.023 & 0.037 & 0.077 & 0.153 & -- \\
        &      & Accuracy  & 0.007 & 0.008 & 0.008 & 0.006 & 0.003 & $\minus 0.034$ & -- \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%
